Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-13 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
switched to eval = TRUE for git2r code

  iheatmapr::add_main_heatmap(ann2, name = "signal2", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_main_heatmap(ann1, name = "signal1", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_row_annotation(ann5, side = "left") %>%
    iheatmapr::add_col_labels() %>%
  iheatmapr::add_row_annotation(ann4, side = "left") %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_row_annotation(ann6, side = "left") %>%
    iheatmapr::add_row_labels()

>>>>

  iheatmapr::add_main_heatmap(ann2, name = "signal2", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_main_heatmap(ann1, name = "signal1", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_row_annotation(ann5, side = "left") %>%
    iheatmapr::add_col_labels() %>%
  iheatmapr::add_row_annotation(ann4, side = "left") %>%
  iheatmapr::add_row_annotation(ann6, side = "left") %>%
    iheatmapr::add_row_labels()
